Analysis of professional surfing tournaments with generalized Bradley-Terry

### 2021-08-12 inst/surfing.Rmd
more work on surfing paper

```{r dosameptest, cache=TRUE}
samep.test(surfing, c("Ferreira","Medina"))
samep.test(surfing, c("Ferreira","Florence"))
samep.test(surfing, c("Florence","Medina"))
samep.test(surfing, c("Florence","Medina","Ferreira"))
```

@@

```{r plotwidep}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype",ylab="support")
```

>>>>

```{r dosameptest, cache=TRUE}
samep.test(surfing, c("Ferreira","Medina"))
samep.test(surfing, c("Ferreira","Florence"))
samep.test(surfing, c("Florence","Medina"))
samep.test(surfing, c("Florence","Medina","Ferreira"))
samep.test(surfing, c("Medina","Wilson"))
```

@@

```{r plotwidep}
plot(c(0,p_wide),c(l0,l_wide)-max(l),type='b',xlab="Brazilian beachtype wide",ylab="support")
abline(h= -2,lty=2)
```

### 2021-08-12 inst/surfing_jsa.tex
more work on surfing paper

\[
\left(\frac{p_1+p_H}{p_1+p_2+p_H}\right)^a
\left(\frac{p_1}{p_1+p_2+p_H}\right)^b
\left(\frac{p_2+p_H}{p_1+p_2+p_H}\right)^c
\left(\frac{p_2+p_H}{p_1+p_2+p_H}\right)^d,
\]

@@

>>>>

\begin{equation}\label{home_ground_advantage}
\left(\frac{p_1+p_H}{p_1+p_2+p_H}\right)^a
\left(\frac{p_1}{p_1+p_2+p_H}\right)^b
\left(\frac{p_2+p_H}{p_1+p_2+p_H}\right)^c
\left(\frac{p_2+p_H}{p_1+p_2+p_H}\right)^d,
\end{equation}

@@

We may ask whether the top two officially ranked competitors, Medina
and Ferreira, have different strengths.  To test the null of equal
strength, we maximize the likelihood subject to the null, and compare
with the global maximum likelihood~\cite{hankin2010}.  This gives us a
support difference of about 0.05, well short of Edwards's 2 units of
support criterion.  Alternatively, we could observe that the
$-2\log\left(\frac{\Lambda}{\Lambda_0}\right)\simeq 0.1$ is not in the tail
region of its asymptotic $\chi^2_1$ distribution.  We may thus assert
that there is no strong evidence for Ferreira's actually having a
competitive advantage over Medina.  {\bf Tim: how about comparing
  Medina with, say, Wilson, would that make sense from a surfing
  perspective? Tim can you say something about Wilson's rivalry with
  Medina?}  We may similarly wonder whether Medina is equal in
strength to Wilson; here we reject the null with support difference of
about 2.33, corresponding to a $p$-value of $0.031$.

\section{Brazilian beach type prefereneces}

The statistical method described here can test many different
suggestions drawn from surfing lore {\bf Tim is there a better way to
  describe this?}.  For example, one frequent suggestion {\bf Tim I
  need citations here} is that Brazilian surfers such as Ferreira and
Toledo have surfing skillsets that favour point and beach break
beaches, those types of beach being readily accessible to these
surfers' native Brazil.  We now assess the null that Brazilians
perform equally well on all types of beaches.  To that end, we create
a reified surfer, ``Brazilian beachtype", whose strength helps all
Brazilian surfers when surfing on their (putative) preferred
beachtype, analogously to the ``home ground monster" who helps the
home team as per equation~\ref{home_ground_advantage}.  The null would
be that this reified entity has zero strength.  We fail to reject this
null (differential support = 0.035; $p=0.79$) and conclude that there
is no evidence to suggest that Brazilians perform is better on their
preferred beach types than one would expect by chance.  We may go
further and state that not only is the maximum likelihood estimate for
Brazilian beachtype is very small (about 0.002), but we may rule out
the suggestion that the strength of this entity exceeds about 0.025
(Figure~\ref{brazilian_beachtype_support}).

\begin{figure}
  \includegraphics[width=4in]{surfing_files/figure-html/plotwidep-1.png}
\caption{Support \label{brazilian_beachtype_support} for the Brazilian beachtype reified entity}
\end{figure}

\section{Compatriot selection}
